\section{Asymptotic Studies and Dispersive Effects} 
\tstk{Rename when you get the chance, to something more appropriate}

\tstk{linking intro too; here we are going to motivate the idea of critical contrast and how it causes band-gaps and other effects to emerge, when the size of the inclusion is fixed. This will then be a natural point to talk about some of the missing gaps WRT K-Fig studies and the missing ``homogenisation" problem? Then we'll talk about thickened graphs and the limit as width goes to zero. This will motivate our singular structures, and also show that dissipative effects can emerge from geometric, as well as material, properties. Then, this should provide a natural segway into what we are planning to talk about: our starting point of singular structures to introduce contrast effects, the gaps in the literature that this work is related to (is this the limiting problem of some other system?), and our objectives in carrying out this research}

% include the discussion on thin structures
\input{./Chapters/Introduction/Intro-SSThinStructures.tex}

% now begin the discussion of critical contrast
\input{./Chapters/Introduction/Intro-CriticalContrastResonance.tex}

% finally, talk about when both $\delta$ and $\eps$ are present, and lead into Research Overview
\subsection{Double limits in $\eps$ and $\delta$.} \label{ssec:Intro-DoubleLimits}
So far we have considered the result of a shrinking domain thickness given fixed material properties, and then various asymptotic limits of high contrast materials with fixed inclusion sizes. 
It is natural to ask whether any consideration has been put into considering the effects that might emerge when both the (relative) size $\delta$ of the region $Q_1$ shrinks to zero \emph{and} the contrast in the material properties increases to infinity.
The series of papers \tstk{Kuchment-Figotin refs} was dedicated to investigating the spectral properties that emerge in the aforementioned limits, for a variety of operators relevant to models of wave propagation.
This series begins \tstk{scalar model, Kuch-Fig} studying the acoustic equation on a non-magnetic composite material whose period cell $Q$ is the unit square in $\reals^2$, and whose inclusion $Q_0$ is a smaller square of side length $1-\delta$.
The region $Q_1$ is therefore shrinking as $\delta\rightarrow0$ (visually, to a singular structure) and possesses (``dimensionless") dielectric constant $\eps_m$ which is equal to $\eps$ on $Q_1$ and $1$ on $Q_0$.
For sufficiently small values of $\delta$, $\bracs{\delta\eps}^{-1}$, and $\eps\delta^2$, it is demonstrated that spectral gaps open, that the spectrum concentrates near the eigenvalues of the Neumann Laplacian on (the union of all periodic translations of) $Q_0$, and an estimate for the width of the spectral bands is also provided.
This was followed up by \tstk{Maxwell/ photonic crystals study} consideration of the curl-of-the-curl equation in $\reals^3$, on a domain that was the extrusion into 3 dimensions of the 2D domain described previously.
In the asymptotic regime $\eps\delta^{\frac{3}{2}}\ll 1$, $\eps\delta\gg1$, gaps in the spectrum once again begin to open --- details on the structure of the spectrum and estimates regarding the width of the spectral bands are again provided.
Finally, analysis of the acoustic approximation when the region $Q_0$ was a polygon \tstk{check: F-K describe their domain in $\reals^d$, but then I think just work in $d=2$ for the entire paper...} was considered, in the limit as $\delta\rightarrow0$, and $\bracs{\delta\eps}^{-1}\rightarrow W<\infty$. \tstk{obtain a QG problem... also this series of papers and this result appears in Kuchment's review paper too.}
Note that since the region $Q_0$ is a polygon, the region $Q_1$ can be thought of as a thickening of some graph $\graph$ embedded into $\reals^2$.
Under these assumptions, it is shown that the spectrum of the acoustic equation on such a medium converges to the spectrum of the problem
\begin{align} \label{eq:Intro-KuchFigQGLimit}
	-\laplacian u &= \lambda\bracs{\delta_{\graph} + W}u,
\end{align}
where $\lambda$ is the spectral parameter and $\delta_{\graph}$ is the delta function supporting the graph $\graph$.
Note that this convergence is not in the norm-resolvent sense, and only demonstrates coincidence of the limit of the acoustic equation as $\delta\rightarrow0$, $\bracs{\delta\eps}^{-1}\rightarrow W<\infty$ with the spectrum of the problem \eqref{eq:Intro-KuchFigQGLimit}.
This is of particular interest to our work in chapter \ref{ch:SingInclusions}, where we will consider a composite medium with one of the components being a singular structure, and look to obtain (and solve) a non-local quantum graph problem from our singular structure formulation.
However we note that our approach via singular structures is motivated by geometric contrasts, rather than the combination of geometric and material contrasts that these studies consider.
\tstk{anything that goes beyond these studies? I don't think there is.}