\section{Mathematical Treatment of Composite, Periodic Media} \label{sec:MathHomLR}
\tstk{this is the section where I plan to talk about how band-gaps, 2-composite media, etc, have been treated in the mathematical community. Also need to talk about work on thin structures, and setup the stage for convergence to QGs.}

%At their heart, photonic crystals are simply periodic mediums whose period cell consists of a set of (dielectric material) inclusions embedded into another (background, or ``matrix") material.
%With developing interest in designing photonic crystals, there have been a number of studies dedicated to understanding the factors which contribute to the opening of spectral band gaps in periodic, composite media (the wider class of materials into which photonic crystals fall).
Before discussing the relevant results in the literature, we provide a toy setup for the study of wave propagation in a composite, periodic medium, to aid in contextualising what follows.
A suitable governing equation for wave propagation is the wave equation;
\begin{align*}
	-\grad\cdot A(x)\grad u(x,t) &= \pdiff{u}{t}(x,t),
\end{align*}
where $A(x)$ represents the material properties relevant to wave propagation, and is spatially varying if the material is non-homogeneous.
For example, in the acoustic setting $A$ would represent the ratio of the elastic modulus and mass density, whilst in the electromagnetic setting would represent the (inverse) product of the electric permittivity and magnetic permeability.
Although a good starting point, we note that the wave equation is not capable of describing all the dynamics of wave propagation in electromagnetic and acoustic settings --- where one would need to consider the Maxwell system or equations of elasticity, which are vectorial.
Indeed the scalar wave equation typically emerges as a special case of these vectorial systems; in the context of electromagnetism in absence of wave sources each component of the electric field vector satisfies the scalar wave equation, for example.

Seeking a Bloch wave solution $u(x,t) = \hat{u}(x)\e^{\rmi\omega t}$ and de-dimensionalising the wave equation via $y=lx, l>0$\footnote{In the event we are looking at a finite medium, $l$ is typically the spatial extent of the medium. For studying periodic materials, $l$ can typically be taken to be the period of the medium so that the period cell has unit non-dimensional length.} and $a(y) = \hat{A}A(x/l)$, one obtains the eigenvalue problem
\begin{align*}
	-\grad_{y}\cdot a\bracs{y}\grad_{y} U(y) = z U(y),
	&\qquad 
	z = \frac{\omega^2 l^2}{\hat{A}},
\end{align*}
where $U(y)=\hat{u}(x/l)$.
In the event that $a$ is constant, the parameter $z$ represents (up to a constant) the square of the ratio of the spatial extent of the medium against the wavelength of propagating waves.
In the electromagnetic setting for example, one has
\begin{align*}
	z &= \frac{l^2 \omega^2 \eps_\mathrm{r}\mu_{\mathrm{r}}}{c^2},
\end{align*}
where $\eps_\mathrm{r},\mu_{\mathrm{r}}$ are the relative permittivity and permeability of the medium.
As such, throughout this work we will consider the (de-dimensionalised) ``wave equation" (more precisely Helmholtz equation) to be the equation
\begin{align*}
	-\grad\cdot a(x)\grad u(x) &= \omega^2 u(x), \qquad x\in\ddom,
\end{align*}
on some suitable domain $\ddom$, and we will also illustrate some of the concepts from the relevant literature using this equation as an example.
Working with non-dimensional units also allows to qualitatively describe the structure of the spectrum of these problems, and the physically-inclined reader can then obtain the physical wave-frequencies by reversing the process described above.
In a slight abuse of notation, we will continue to use $\omega^2 = z$ for the spectral parameter as it will be convenient for us to use the square-root of $z$ at certain points in what follows.

At their heart, photonic crystals are simply periodic materials whose period cell consists of a set of (dielectric material) inclusions embedded into another (background, or ``matrix") material.
With developing interest in designing photonic crystals, there have been a number of studies dedicated to understanding the factors which contribute to the opening of spectral band gaps in periodic, composite media (the wider class of materials into which photonic crystals fall).
Mathematically, a periodic composite medium can be modelled by filling the space $\reals^d$ with translations of a period cell $Q=[0,1)^d$ that is further divided into two regions, the ``inclusion" $Q_0$ and ``background" $Q_1$ with $\overline{Q_0}\subset Q$ and $Q_1=Q\setminus\overline{Q_0}$.
One also typically specifies the relative size of the inclusion to the size of the period cell, which we will denote by $0<l<1$ (so if the side of the period cell is of unit length, the inclusion $Q_0$ has volume of the order $l^d$).
The material properties are then represented by a $Q$-periodic function $a(x)$;
\begin{align*}
	a(x) &= \begin{cases} a & x\in Q_i, \\ 1 & x\in Q_j, \end{cases}
	\qquad i,j\in\clbracs{0,1}, \ i\neq j.
\end{align*}
with the regions $Q_0$ and $Q_1$ typically labelled the ``soft" (where $a(x)=a$) and ``stiff" ($a(x)=1$), and the constant $a$ representing the contrast between the material parameters.
Along with a governing equation such as the wave equation, one is then looking to determine or examine those pairs $z, U$ that satisfy the governing equation, with any ``gaps" in $z$ representing spectral band gaps that the composite material possesses, and relate the emergence of these gaps back to relations between quantities such as the material contrast $a$ or inclusion-volume fraction $l$.

The periodic nature of the material properties (encoded in the function $a(x)$) and the desire to understand the effective properties of the medium naturally lends itself to study through the process of homogenisation.
Broadly speaking, homogenisation theory looks to take a problem on an inhomogeneous material and derive an ``effective" problem for that material (in some limit) in terms of the ``homogenised" material properties, and establish convergence results for the solution of the original problem to those of the effective problem.
This allows a potentially complex problem to be approximated by a system more tractable to analysis, and the establishment of convergence results ensures that the approximation is valid under certain parameter regimes.
We will attempt to illustrate some of these frameworks; suppose our interest lies in studying the eigenvalues of the wave equation
\begin{align*}
	\mathcal{A}u &:= -\grad\cdot a(x)\grad u = \omega^2 u, \qquad x\in\reals^d,
\end{align*}
where $\reals^d$ is filled with a periodic, composite medium with unit cell $Q=Q_0\cup Q_1$ as described above.
To approximate the spectrum of $\mathcal{A}$ at high frequency, we introduce the parameter $\eps\ll 1$ and consider the problem
\begin{align*}
	\mathcal{A}_{\eps}u_{\eps}(x) &:= -\grad\cdot a\bracs{\frac{x}{\eps}}\grad u_{\eps}(x) = \omega^2 u_{\eps}(x), \qquad x\in\ddom_{h}:=[0,1)^d,
\end{align*}
with periodic boundary conditions on $\ddom_h$, in the limit as $\eps\rightarrow0$.
Using the theory and techniques from homogenisation theory, we would look to derive an effective problem of the form
\begin{align*}
	\mathcal{A}_0 u_0(x) &:= -\grad\cdot a_{\mathrm{hom}}\grad u_0(x) = \omega^2 u_0(x), \qquad x\in\ddom_h,
\end{align*} 
where $a_{\mathrm{hom}}$ is no longer spatially varying, and represents the homogenised material properties.
We would then look to study this effective problem, and prove convergence (in an appropriate norm) of the spectrum of the operator $\mathcal{A}_{\eps}$ to that of $\mathcal{A}_0$.
The convergence results ensure that $\mathcal{A}_0$ serves as a faithful approximation to our original problem, and thus its behaviour is reflective of the original problem we set out to model.
We can also attempt to derive an effective dispersion relation, or spectral structure from this effective system to make inferences about the properties of waves within the medium.
Alternative frequency approximations, such as the finite frequency approximation, are also realisable and adhere to a similar ethos.
In the finite frequency regime, we introduce the length scale $L>0$ and form the domain
\begin{align*}
	\ddom_f &= \bigcup_{T\in\clbracs{0,...,L}^d}\bracs{Q + T}\subset[0,L)^d,
\end{align*}
again imposing periodic boundary conditions, and study the ``limit" of the problem
\begin{align*}
	\mathcal{A}_L u_L(x) &:= -\grad\cdot a(x)\grad u_L(x) = \omega^2 u_L(x), \qquad x\in\ddom_f
\end{align*}
as $L\rightarrow\infty$.
The two regimes are related through appropriate length and frequency scaling, indeed if we make the domain-length-scale substitution $y = \frac{x}{\eps}$ into the high frequency problem we observe that
\begin{align*}
	-\grad\cdot a\bracs{\frac{x}{\eps}}\grad u_{\eps}(x) &= \omega^2 u_{\eps}(x), &\qquad x\in\ddom_h, \\
	\Leftrightarrow -\eps\grad_{y}\cdot \eps a(y)\grad_{y}u_{\recip{\eps}}(y) &= \omega^2 u_{\recip{\eps}}(y), &\qquad y\in\ddom_f.
\end{align*}
Thus, we can transition between the high and finite frequency approximations using the length and frequency scale transforms $x \mapsto \eps x$ and $\omega \mapsto \frac{\omega}{\eps}$.


The existence of spectral gaps, and the extent of control one can exert on them through the material parameters, has been the subject of several studies.
The study in \tstk{Fig. Kuchment: Band-Gap structure of periodic dielectric and acoustic media (scalar)} focused on the spectrum of the operator $-\grad\cdot a\bracs{y}\grad$ for a composite, periodic medium with $Q=[0,1)^3$, and stiff inclusions $Q_0$ being cubes of side length $1-\delta$.
Provided that $\delta, a\delta^{-1}$ and $a^{-1}\delta^2$ are sufficiently small, the existence of spectral gaps was found to be guaranteed, and could even be opened up in any finite part of the spectrum.
A follow-up study \tstk{F.Kuch: Band-gap structure of the spectrum of periodic Maxwell operators} established similar results on existence of spectral band gaps for the \tstk{defn? F and K considered $\curl{}\bracs{a(x)\curl{}}$ in that study, can't really call it Maxwell operator though} in a similar material.
\tstk{now onto critical contrast, and homogenisation. Why is homogenisation relevant (need to establish finite frequency approximation setup too)? What is critical contrast (scaling of the inclusion volume ratio to the material properties)? How does it relate to the study of photonic crystals and/or metamaterials? The critical contrast and volume ratio of the inclusions shrinking to zero then brings us nicely on towards singular inclusions and Exner-Post, K-Zheng in the next section too.}