\chapter*{Acknowledgements}
I would like to say a huge thank you to everyone who has supported me over the course of my PhD.
If you've ever had the (dis)pleasure of meeting me in person, you'll know that I'm awful when it comes to writing about these sorts of things.
Me attempting to write prose will turn this section into an incoherent mess, so to everyone listed below a massive thank-you for the support you have provided, in every capacity.

My supervisor Kirill for the past four years of guidance and advice, and encouraging me to join the department through SAMBa in the first place.
Also to Susie, Jess, and Helena for all their help with settling in to SAMBa, getting me involved with activities like the conference and induction training, and continued support and reassurance through to the end of my PhD.

Mum, Dad, Arthur, and Cassie for their continuous support for me throughout my PhD.
Special thanks to Mum and Dad and for tolerating my decision to postpone my entry into ``the real world, where people have jobs" for an additional 4 years.

Sam, for many enjoyable conversations, games evenings, FPL thrashings, and pub trips --- and who probably deserves a medal for surviving three years of living with me. 
The same medal needs to go to Chris during undergraduate, and for a friendship that has continued since.

Abi and Michael, for many an enjoyable board games evening, trip out, and the occasional (highly controversial) mini-golf game --- and continuing to talk to me despite my best efforts to sabotage our undergraduate degrees with procrastination...

Ivan, for providing encouragement and reassurance during the final stages of my research and write up. 
And additionally Rebecca, Lisa, Flo, R\'{e}my, and George for all the times I've been able to visit, and for not forgetting about me on the other side of the country.

Cameron for all the lunchtime think tanks and four years of PhD guidance, Barry (who upon reading this will know she's one board game richer), Jack \& Will for all the programming help and getting me involved with teaching outside the department, and my wonderful desk-neighbours Pawel \& Yvonne (and by the nearest-neighbour metric, Fraser).
Additional thanks to all the PhD students and PostDocs in the department and wider university community that I've had the pleasure to know over the last four years; the regulars at Wednesday cake, DitP (hail emperor Kat) and SAMBa coffee, and everyone from the maths football team --- we'll just skim over the fact that I'm leaving with a net goal deficit... 

And now, onto the thesis.
You might ask why would you ever want to read $150+$ pages of maths written by me.
Well look, I'll be honest with you, I have no idea --- \emph{but} I'm sure we can find something worth your time...